The title

### 2019-07-26 README.Rmd
fixed README

The goal of qtl2hotspots is to analyze the Keller et al. (2018) expression trait hotspots.

@@

To render the manuscript `paper.Rnw`, into pdf, use a shell to enter the following text from the 'hotspots' directory:

@@

If you're not using Docker, and have cloned the repository from Github, you can use the Makefile to render `paper.Rnw`. Just type `make` in the shell (from within the `hotspots` directory):

@@

Please note that the 'qtl2hotspots' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

>>>>

The goal of `qtl2hotspots` is to analyze the Keller et al. (2018) expression trait hotspots with both mediation methods and pleiotropy tests.

@@

To render the manuscript `paper.Rnw`, into pdf, use a shell to enter the following text from the `qtl2hotspots` directory:

@@

If you're not using Docker, and have cloned the repository from Github, you can use the Makefile to render `paper.Rnw`. Just type `make` in the shell (from within the `qtl2hotspots` directory):

@@

Please note that the `qtl2hotspots` project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
